---
<<<<<<< HEAD
title: "PA1_template.Rmd"
author: "Tom Ward"
date: "7/16/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(lattice)
```

Read the file into a dataframe using read.csv:

```{r read, echo=TRUE}
df <- read.csv("activity.csv")
```


```{r mean, echo=TRUE}
steps <- group_by(df,date)
steps_summ <- summarise(steps,sum_steps = sum(steps))
hist(steps_summ$sum_steps, col = "green",main = "Histogram of Total Number of Daily Steps",xlab = "Total Number of Daily Steps")
step_mean <- mean(steps_summ$sum_steps,na.rm = TRUE)
step_median <- median(steps_summ$sum_steps,na.rm = TRUE)
```

The mean total number of steps is `r step_mean`.

The median total number of steps is `r step_median`.

```{r intervals, echo=TRUE}

avg_df <- group_by(df,interval)
int_df <- summarise(avg_df,avg_steps_int = mean(steps,na.rm = TRUE))
plot(int_df$interval,int_df$avg_steps_int,type="l",xlab="Interval",ylab="Average Steps Per Interval")

high <- max(int_df$avg_steps_int)

```

The highest total number of steps for an interval on average was `r high`.

```{r missing_values, echo=TRUE}

number_of_nas <- sum(is.na(df))
df1 <- df
df1$steps[which(is.na(df1$steps))] <- mean(df1$steps,na.rm = TRUE)
steps_imputed <- group_by(df1,date)
steps_imputed_summ <- summarise(steps_imputed,sum_imputed_steps = sum(steps))
hist(steps_imputed_summ$sum_imputed_steps,main="Histogram of Total Steps with Imputed Values",xlab="Total Steps")
mean_imp <- mean(steps_imputed_summ$sum_imputed_steps,na.rm = TRUE)
median_imp <- median(steps_imputed_summ$sum_imputed_steps,na.rm = TRUE)

```

There are `r number_of_nas` rows that contain NAs.

After imputing values using the average number of steps across intervals, the mean is `r mean_imp` and the median is `r median_imp`. 

```{r weekdays, echo=TRUE}

df$date <- as.Date(df$date)
df$day_type <- weekdays(df$date)
df$week[df$day_type == "Monday"] <- "Weekday"
df$week[df$day_type == "Tuesday"] <- "Weekday"
df$week[df$day_type == "Wednesday"] <- "Weekday"
df$week[df$day_type == "Thursday"] <- "Weekday"
df$week[df$day_type == "Friday"] <- "Weekday"
df$week[df$day_type == "Saturday"] <- "Weekend"
df$week[df$day_type == "Sunday"] <- "Weekend"

avg_df <- group_by(df,interval,week)
int_df <- summarise(avg_df,avg_steps_int = mean(steps,na.rm = TRUE))
xyplot(avg_steps_int ~ interval|week,data = int_df, type="b",ylab="Number of steps",xlab="Interval")

```


=======
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
>>>>>>> 80edf39c3bb508fee88e3394542f967dd3fd3270
